\documentclass[../main.tex]{subfiles}
\begin{document}

\section{Academic Research Projects}
  \vspace{3pt}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Final-Year Thesis, Nanyang Technological University}{}
      {Grade: A+ | Principal Investigator: John Tan, PhD \& Sofyan Sahrom, PhD}{Apr 2022 - Nov 2022}
        \resumeItemListStart
            \resumeItem{Collaborated with National Youth Sports Institute and Singapore Weightlifting Federation.}
            \resumeItem{Led the application of research ethics and designed the study protocol of evaluating the validity of a velocity-based training device in weightlifting exercises using VICON 3D motion capture cameras [\textcolor{blue}{P\ref{article: fyp}}].}
            % \resumeItem{Utilized VICON 3D motion capture cameras.}
            \resumeItem{Wrote a MATLAB script to efficiently extract data from c3d files to perform Bland-Altman analysis [\href{https://github.com/Shahril-Iskandar/undergraduate-finalyearproject}{\faGithub}].}
            \resumeItem{Received the \href{https://drive.google.com/file/d/1kLCyjZXhJKm-lV7M_6sJ5hKYgOW0xfY2/view?usp=sharing}{Best Poster} Presentation \href{https://drive.google.com/file/d/1mcvcseOSgvzBLQg3tZVkGyIOOxVw6gKw/view?usp=sharing}{award} at the 11$^{th}$ Lau Teng Chuan Physical Education \& Sports Science Symposium.}
        \resumeItemListEnd

    % \newpage

    \resumeSubheading % “A Video-Based Treadmill Running Analysis Model”
      {Undergraduate Research Programme  \href{https://www.ntu.edu.sg/education/undergraduate-research-experience-on-campus-(ureca)}{(URECA)}, Nanyang Technological University}{}
      {Sports Biomechanics Lab | Principal Investigator: Kong Pui Wah, PhD}{Aug 2021 - Aug 2022}
        \resumeItemListStart       
            \resumeItem{Contributed to the development of a video-based analysis model for assessing treadmill running biomechanics.}
            \resumeItem{Facilitated over 40 participants' recruitment and utilized Kinovea to analyze running kinematics.}
            \resumeItem{Presented findings at 2 academic conferences [\textcolor{blue}{CP\ref{conference_pre: isbs2022}}, \textcolor{blue}{CP\ref{conference_pre: icur2022}}] and published 2 journal articles [\textcolor{blue}{J\ref{article: paah foot morphology}}, \textcolor{blue}{J\ref{article: frontiers foot inversion}}].}
            \resumeItem{Conferred the title “\href{https://drive.google.com/file/d/1Ut1poXJ_C8lSSeckPBVFy2DgOusebh7V/view?usp=sharing}{NTU President Research Scholar}” for completing the programme with Distinction.}
        \resumeItemListEnd
        
    \resumeSubheading
      {Final-Year Thesis, Republic Polytechnic}{}
      {Grade: A | Principal Investigator: Shigetada Kudo, PhD \& Alexander Ong, PhD}{Apr 2016 - Oct 2016}
        \resumeItemListStart
            \resumeItem{Collaborated with Singapore Sports Institute and Singapore Swimming Association.}
            % \resumeItem{Utilized a video camera to capture 3 youth athletes’ diving movements.}
            \resumeItem{Conducted springboard diving kinematics analysis using 2 software, Kinovea and Mokka.}
            \resumeItem{Presented findings to the coach.}
        \resumeItemListEnd
        
  \resumeSubHeadingListEnd

\end{document}