\documentclass[../main.tex]{subfiles}
\begin{document}

% In press = accepted, not yet published
% under review = waiting for reviewer comments
% Submitted = no news from editor yet
%\small \normalfont ($^\dagger$ indicates equal contribution)
% \href{https://scholar.google.com.sg/citations?user=ZQ5Z5YIAAAAJ&hl=en}{\faGoogleScholar}

\section{Publications} 
  \vspace{2pt}
  \resumeSubHeadingListStart
    \item
        \small \normalfont * indicates corresponding author
        % \small \normalfont {$^\dagger$ indicates equal contribution}
    \item
        \textbf{Peer-reviewed Journal Articles} \orcidlink{0000-0002-8037-2458} 
        \def\labelprefix{J}
        \begin{etaremune}
            \item\label{article: spm exoskeleton}{Kong, P. W.*, Koh, A. H., Ho, M. Y. M., \textbf{Iskandar, M. N. S.}, \& Lim, C. X. E. (2024). Effectiveness of A Passive Military Exoskeleton in Offloading Weight during Static and Dynamic Load Carriage: A Randomised Cross-Over Study. \textit{Applied Ergonomics}. 119, 104293. doi: \nolinkurl{10.1016/j.apergo.2024.104293} \href{https://doi.org/10.1016/j.apergo.2024.104293}{\faFilePdfO} \href{https://github.com/Shahril-Iskandar/publication-exoskeleton}{\faGithub}}

            \item\label{article: frontiers crossover gait} {\textbf{Iskandar, M. N. S.}, Loh, R. B. C., Ho, M. Y. M., Pan, J. W. \& Kong, P. W.* (2023). Crossover Gait in Running and Measuring Foot Inversion Angle at Initial Foot Strike: A Front-View Video Analysis Approach. \textit{Frontiers in Bioengineering and Biotechnology}. 11, 1210049. doi: \nolinkurl{10.3389/fbioe.2023.1210049} \href{https://doi.org/10.3389/fbioe.2023.1210049}{\faFilePdfO} \href{https://github.com/Shahril-Iskandar/publication-crossover-gait}{\faGithub}} % At time of publishing, IF 5.7, Citescore: 6.7
            
            \item\label{article: sensors validation exoskeletal} {Kong, P. W.*, \textbf{Iskandar, M. N. S.}, Koh, A. H., Ho, M. Y. M., \& Lim, C. X. E. (2023). Validation of In-Shoe Force Sensors During Loaded Walking In Military Personnel. \textit{Sensors}. 23(14), 6465. doi: \nolinkurl{10.3390/s23146465} \href{https://doi.org/10.3390/s23146465}{\faFilePdfO} \href{https://github.com/Shahril-Iskandar/publication-loadsol-validation-military}{\faGithub}} % At time of publishing, IF 3.9, Citescore: 6.8
            
            \item\label{article: paah foot morphology} {Pan, J. W., Ho, M. Y. M., Loh, R. B. C., \textbf{Iskandar, M. N. S.}, \& Kong, P. W.* (2023). Foot Morphology and Running Gait Pattern between the Left and Right Limbs in Recreational Runners. \textit{Physical Activity and Health}, 7(1), 43–52. doi: \nolinkurl{10.5334/paah.226} \href{https://doi.org/10.5334/paah.226}{\faFilePdfO}} % At time of publishing, IF 3.1, Citescore: 4.5
        \end{etaremune}
                
        \textbf{Peer-reviewed Conference Proceeding}
        \def\labelprefix{C}
        \begin{etaremune}
            \item\label{conference: isbs2024opencap} {\textbf{Iskandar, M. N. S.}, \& Teng, P. S. P.* (Accepted). Kinematics Comparison of OpenCap and IMU with Marker-Based Motion Capture In Treadmill Running: A Pilot Study. \textit{Proceedings of the 42$^{nd}$ International Society of Biomechanics in Sports Conference.} \href{https://github.com/Shahril-Iskandar/publication-conference-validation}{\faGithub}}
        
            \item\label{conference: isbs2024raystudy} Loh, R. B. C., Ho, M. Y. M., {\textbf{Iskandar, M. N. S.}, \& Kong, P. W.* (Accepted). Two-Dimensional Kinematics Differences Between Sexes In Runners With and Without Patellofemoral Pain. \textit{Proceedings of the 42$^{nd}$ International Society of Biomechanics in Sports Conference.}}
            
            \item\label{conference: isbs2022} {\textbf{Iskandar, M. N. S.}, Loh, R. B. C., Ho, M. Y. M., Pan, J. W., \& Kong, P. W.* (2022). Comparison of Rearfoot Inversion Angle at Initial Footstrike Measured From Front And Back View Videos. \textit{Proceedings of the 40$^{th}$ International Society of Biomechanics in Sports Conference}, 40(1), 291. \href{https://commons.nmu.edu/isbs/vol40/iss1/70/}{\faFilePdfO}}
        \end{etaremune}

        \textbf{Conference Abstract}
        \def\labelprefix{CA}
        \begin{etaremune}
            \item\label{conference_abstract: cherylMilitary} {Lim, C., Kong, P. W., Koh, A. H., Ho, M., \& \textbf{Iskandar, M. N. S.}. The physiological and biomechanical effects of a full-body passive exoskeleton on military load carriage. \textit{6th International Congress on Soldiers' Physical Performance}. September 2023. {\href{https://cdn.asp.events/CLIENT_CLDD_9BDAB70C_5056_B733_4934A7872C9C46B0/sites/dsei-2023/media/ICSPP_program_book.pdf}{\faFilePdfO}}}

            \item\label{conference_abstract: assbLoadsolValidation} {\textbf{Iskandar, M. N. S.}, Koh, A. H., Ho, M. Y. M., Lim, C. X. E., \& Kong, P. W. Validation of the loadsol® in-shoe force sensors during walking in military boots under heavy load carriage. \textit{9$^{th}$ Asian Society of Sport Biomechanics Conference}. August 2023. }
            
            \item\label{conference_abstract: rayReliability} {Loh, R. B. C., Ho, M. Y., \textbf{Iskandar, M. N. S.}, Pan, J. W., \& Kong, P. W. Reliability of video-based running gait analysis in recreational runners. \textit{XXII International Conference on Mechanics in Medicine and Biology}. August 2022.}
        \end{etaremune}
        
        \textbf{In Progress}
        \def\labelprefix{P}
        \begin{etaremune}                     
            \item\label{article: diffusion_openpose}{Zhou, T., \textbf{Iskandar, M. N. S.}, \& Chiam, K. H.* (Under Review). Diffusion Models Enable Zero-Shot Pose Estimation for Lower-Limb Prosthetic Users. \href{https://arxiv.org/abs/2312.07854}{\faFilePdfO}}
            
            \item\label{article: fyp}{\textbf{Iskandar, M. N. S.}*, Tan, J. C. C., Wong, H., Low, A., \& Sahrom, S. B. (In preparation). Criterion Validity of The FLEX Device Measuring Barbell Velocity in Weightlifting Exercises Across the Load-Velocity Profile. \href{https://github.com/Shahril-Iskandar/publication-validity-flex-vbt}{\faGithub}}
        \end{etaremune}
        
  \resumeSubHeadingListEnd

\end{document}