\documentclass[../main.tex]{subfiles}
\begin{document}

\section{Research Experience}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Senior Research Assistant, Nanyang Technological University}{Singapore}
      {Sports Biomechanics Lab | Principal Investigators: Phillis Teng, PhD \& Kong Pui Wah, PhD}{Aug 2023 - Feb 2025}
        \resumeItemListStart
            \resumeItem{Assisting in 2 main projects; 1) Screening and Biomechanical Risk Factors for Early Knee Osteoarthritis, 2) Coaching table tennis to individuals with physical disabilities.}
            \resumeItem{Contributing to the development of the research design and ethics application.}
            % \resumeItem{The project aims to develop a novel screening method to identify biomechanical markers for recreational runners identified to be at risk of early knee osteoarthriti.s}
            \resumeItem{Conducting a systematic review on the use of ultrasonography to diagnose early knee osteoarthritis using Covidence.}
            \resumeItem{Mentoring and coordinating with 2 undergraduate students in data collection in utilizing various equipment such as plantar pressure mapping, tensiomyography and thermal camera.}
            % \resumeItem{Developing a R script to automatically create different mask region of the foot after obtaining data from Novel Pedar insoles.}
            % \resumeItem{Facilitating recruitment of participants and data analysis.}
            \resumeItem{Investigating the use of monocular camera to obtain biomechanical data in table tennis through markerless motion capture.}
            \resumeItem{Published a first-author conference paper on the use of markerless motion capture system in running [\textcolor{MidnightBlue}{C\ref{conference: isbs2024opencap}}].}
        \resumeItemListEnd
  
    \resumeSubheading % “Data-driven gait rehabilitation of amputees”
      {Research Intern, Agency for Science, Technology and Research, Bioinformatics Institute}{Singapore}
      {Biophysical Modelling Lab | Principal Investigator: Chiam Keng Hwee, PhD}{Jan 2023 - Jun 2023}
        \resumeItemListStart
            \resumeItem{Contributed to a project on data-driven gait rehabilitation of lower limb amputees.}
            \resumeItem{Implemented generative AI using Stable Diffusion to enhance existing open-source pose estimation algorithm (OpenPose \& DeepLabCut) in identifying lower limb amputee's anatomical landmarks for gait analysis [\textcolor{MidnightBlue}{J\ref{article: diffusion_openpose}}].}
            \resumeItem{Involved in sourcing of walking videos, labeling of anatomical landmarks and training a model using DeepLapCut.}
            \resumeItem{Wrote a Python script to perform data processing and analysis.}
            % \resumeItem{Related publication: P\ref{article: astar internship}}
        \resumeItemListEnd
    
    \resumeSubheading
      {Undergraduate Research Assistant, Nanyang Technological University}{Singapore}
      {Sports Biomechanics Lab | Principal Investigator: Kong Pui Wah, PhD}{Apr 2022 - May 2023}
        \resumeItemListStart
            \resumeItem{Contributed to a project analyzing the biomechanical effects of exoskeletal in military personnel.}
            \resumeItem{Assisted in the synchronized gait data collections using VICON Nexus on Bertec split-belt instrumented treadmill, Delsys EMG system and loadsol® sensors.}
            \resumeItem{Wrote MATLAB and Python scripts to extract data and conduct data analysis of ground reaction forces using statistical parametric mapping, \href{https://spm1d.org/}{spm1d}. \href{https://github.com/Shahril-Iskandar/publication-exoskeleton}{\faGithub}}
            \resumeItem{Publications: 2 conference abstract [\textcolor{MidnightBlue}{CA\ref{conference_abstract: assbLoadsolValidation}}, \textcolor{MidnightBlue}{CA\ref{conference_abstract: cherylMilitary}}] and 2 journal articles [\textcolor{MidnightBlue}{J\ref{article: sensors validation exoskeletal}}, \textcolor{MidnightBlue}{J\ref{article: spm exoskeleton}}].}
            % \resumeItem{{Presented findings at an academic conference [\textcolor{MidnightBlue}{CP\ref{conference_pre: assb2023}}], co-authored a journal article [\textcolor{MidnightBlue}{J\ref{article: sensors validation exoskeletal}}]} and in preparation for another manuscript [\textcolor{MidnightBlue}{P\ref{article: spm exoskeleton}}].}
        \resumeItemListEnd

    % \newpage

    % \resumeSubheading
    %   {Honors Thesis (Grade: A+), Nanyang Technological University}{Singapore}
    %   {Sports Biomechanics Lab | Principal Investigators: John Cher Chay Tan, PhD \& Sofyan Sahrom, PhD}{Apr 2022 - Nov 2022}
    %     \resumeItemListStart
    %         \resumeItem{Collaborated with National Youth Sports Institute and Singapore Weightlifting Federation.}
    %         \resumeItem{Led the application of research ethics and designed the study protocol of evaluating the validity of a velocity-based training device in weightlifting exercises using VICON 3D motion capture cameras [\textcolor{MidnightBlue}{P\ref{article: fyp}}].}
    %         % \resumeItem{Utilized VICON 3D motion capture cameras.}
    %         \resumeItem{Wrote a MATLAB script to extract data from c3d files to perform Bland-Altman analysis. \href{https://github.com/Shahril-Iskandar/undergraduate-finalyearproject}{\faGithub}}
    %         \resumeItem{Awarded Best Poster Presentation \href{https://drive.google.com/file/d/1mcvcseOSgvzBLQg3tZVkGyIOOxVw6gKw/view?usp=sharing}{award} at the 11$^{th}$ Lau Teng Chuan Physical Education \& Sports Science Symposium. \href{https://drive.google.com/file/d/1kLCyjZXhJKm-lV7M_6sJ5hKYgOW0xfY2/view?usp=sharing}{\faFileImageO}}
    %     \resumeItemListEnd

    % \newpage

    \resumeSubheading % “A Video-Based Treadmill Running Analysis Model”
      {Undergraduate Research Programme  \href{https://www.ntu.edu.sg/education/undergraduate-research-experience-on-campus-(ureca)}{(URECA)}, Nanyang Technological University}{Singapore}
      {Sports Biomechanics Lab | Principal Investigator: Kong Pui Wah, PhD}{Aug 2021 - Aug 2022}
        \resumeItemListStart       
            \resumeItem{Contributed to the development of a video-based analysis model for assessing treadmill running biomechanics.}
            \resumeItem{Facilitated over 40 participants' recruitment and utilized Kinovea to analyze running kinematics.}
            \resumeItem{Conferred the title “\href{https://drive.google.com/file/d/1Ut1poXJ_C8lSSeckPBVFy2DgOusebh7V/view?usp=sharing}{NTU President Research Scholar}” for completing the programme with Distinction.}
            \resumeItem{Publications: 2 conference papers [\textcolor{MidnightBlue}{C\ref{conference: isbs2022}}, \textcolor{MidnightBlue}{C\ref{conference: isbs2024raystudy}}], 2 journal articles [\textcolor{MidnightBlue}{J\ref{article: paah foot morphology}}, \textcolor{MidnightBlue}{J\ref{article: frontiers crossover gait}}].}
        \resumeItemListEnd

    \resumeSubheading % Dose-response of leucine on muscle maintenance during weight loss
      {Undergraduate Research Assistant, Nanyang Technological University}{Singapore}
      {Human Bioenergetics Lab | Principal Investigator: Yang Yifan, PhD}{Sep 2020 - Mar 2021}
        \resumeItemListStart
            \resumeItem{Contributed to the project assessing the dose-response of leucine on muscle maintenance during weight loss.}
            \resumeItem{Independently recruited over 20 participants and coordinated weekly anthropometric measurements.} % 18 participants
            % \resumeItem{Provided clear explanations of DEXA scan results to participants.}
            \resumeItem{Verified accuracy of participant's data entry for daily physical activity, sleep, and dietary intake log.}
        \resumeItemListEnd
        
    % \resumeSubheading
    %   {Final-Year Thesis (Grade: A), Republic Polytechnic}{}
    %   {Biomechanics Lab | Principal Investigators: Shigetada Kudo, PhD \& Alexander Ong, PhD}{Apr 2016 - Oct 2016}
    %     \resumeItemListStart
    %         \resumeItem{Collaborated with Singapore Sports Institute and Singapore Swimming Association.}
    %         % \resumeItem{Utilized a video camera to capture 3 youth athletes’ diving movements.}
    %         \resumeItem{Performed 2D kinematic analysis on springboard diving using Kinovea.}
    %         % \resumeItem{Presented findings to the coach.}
    %     \resumeItemListEnd
    
  \resumeSubHeadingListEnd

\end{document}